Still Missing a Cool Title

### 2006-05-31 talk/dls2006/paper.tex
bibtex fixes, a little bibtex boilerplate and one \cite{}.
Added the typesystem graph.

\begin{figure}
\begin{verbatim}
                      RPython
                      /     \
           LLTypeSystem     OOTypeSystem
                  /
          Raw addresses
\end{verbatim}
\caption{Type systems, informally ordered by abstraction level}
\label{fig_typesystems}
\end{figure}

@@

Scheme48 was a Scheme implementation using a restricted Scheme, PreScheme
[PreScheme], with static type inference based on Hindley-Milner.  This is
viable for Scheme as base language.  Simplicity and portability across C
platforms were its major goals.

@@

>>>>

\begin{figure}
\centering
\includegraphics[scale=0.667]{image/typesystems.pdf}
\caption{type systems; the arrows are transformations.}
\label{fig_typesystems}
\end{figure}

@@

Scheme48 was a Scheme implementation using a restricted Scheme, PreScheme
\cite{kelsey-prescheme}, with static type inference based on Hindley-Milner.  This is
viable for Scheme as base language.  Simplicity and portability across C
platforms were its major goals.

@@

\bibliographystyle{abbrv}
\bibliography{paper}
